Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-14 paper/paper.tex
slight tweaks to workflow schematic

\hspace{0.04in} {\bf A} \includegraphics[width=0.9\linewidth, valign=t]{figures/WorkflowSchematic/SchematicForPaper.pdf}
\vspace{0.1in}

@@

\caption{
Single-cell virus sequencing of influenza infections that induce IFN.
{\bf (A)} Experimental workflow.
(1) IFN reporter A549 cells are infected with a mix of wildtype virus and virus carrying synonymous mutations at both ends of each gene segment.
IFN+ cells are enriched by MACS (\FIGSUPP[experiment]{MACS}), and pooled with non-enriched cells and uninfected canine cells that serve as an internal control for multiplets and mRNA leakage.
(2) The mRNAs from individual cells are tagged with cell-specific barcodes using a 10X Chromium device.
(3) The entire cellular transcriptomes are quantified using the standard single-cell mRNA-seq protocol, and viral genes are enriched by influenza-specific PCR and fully sequenced by PacBio.
(4) The result is a matrix giving the expression of each gene in each cell, as well as the full sequences of the viral genes in infected cells.
{\bf (B)} Number of cells for which transcriptomes were obtained.
Most transcriptomes are from human cells, but a few are from the uninfected canine cells spiked into the experiment as a control.
From the transcriptomes with both human and canine transcripts, we estimate~\citep{bloom2018estimating} that $\approx$11\% of the captured cells are actually multiplets in which more than one cell was captured in an emulsion. 
These cross-celltype multiplets are excluded from subsequent analyses.
{\bf (C)} The number of cellular and viral mRNAs detected for each cell is plotted as a point.
Green lines show the distribution of cellular mRNAs per cell, and the blue rug plot at the left of each panel shows the distribution of viral mRNAs per cell.
Cells outside the dashed magenta lines have unusually low or high amounts of cellular mRNA (possibly low-quality emulsions or multiplets), and are excluded from subsequent analyses.
{\bf (D)} Distribution across cells of the fraction of all mRNA derived from influenza.
Cells called as infected are in blue, while other cells are in green.
The inset shows the amount of viral mRNA among the human cells called as infected.
{\bf (E)} The number of influenza genes detected per infected cell, and the amount of viral mRNA in cells expressing each number of viral genes.
The majority of cells express all eight gene segments, but a substantial minority fail to express at least one gene.
\FIGSUPP[experiment]{frac_has_gene} shows the frequency that each viral gene is detected in infected cells.
{\bf (F)} Relative expression of viral genes among infected cells.
{\bf (G)} The number of cells infected with wildtype virus, synonymously barcoded virus, or both.
From the cells infected with both viral barcodes, we estimate~\citep{bloom2018estimating} that 63\% of infected cells are co-infected.
{\bf (H)} Fraction of cellular mRNA derived from type I or type III IFN across all cells, faceted by whether the cells are infected.
Cells to the left of the first dashed magenta line are classified as IFN-, and cells to the right of the second line are classified as IFN+.
We grouped type I and type III IFN together because their expression is highly correlated (\FIGSUPP[experiment]{type_I_III_correlation}).
Many cells that do not express IFN itself still express interferon-stimulated genes (\FIGSUPP[experiment]{ISG}).
}
\label{fig:experiment}

>>>>

\hspace{0.04in} {\bf A} \includegraphics[width=0.95\linewidth, valign=t]{figures/WorkflowSchematic/SchematicForPaper.pdf}
\vspace{0.1in}

@@

\caption{
Single-cell sequencing of influenza infections that induce IFN.
{\bf (A)} Experimental workflow.
(1) IFN reporter A549 cells are infected with a mix of wildtype and synonymously barcoded viruses.
IFN+ cells are enriched by MACS (\FIGSUPP[experiment]{MACS}), and pooled with non-enriched cells and uninfected canine cells that serve as an internal control for multiplets and mRNA leakage.
(2) The mRNAs from individual cells are tagged with cell-specific barcodes using a 10X Chromium device.
(3) The entire cellular transcriptomes are quantified using the standard single-cell mRNA-seq protocol, and viral genes are enriched by influenza-specific PCR and fully sequenced by PacBio.
(4) The result is a matrix giving the expression of each gene in each cell, as well as the full sequences of the viral genes in infected cells.
{\bf (B)} Number of cells for which transcriptomes were obtained.
From the transcriptomes with both human and canine transcripts, we estimate~\citep{bloom2018estimating} that $\approx$11\% of the captured cells are actually multiplets in which more than one cell was in an emulsion. 
{\bf (C)} The number of cellular and viral mRNAs detected for each cell is plotted as a point.
Green lines show the distribution of cellular mRNAs per cell, and the blue rug plot at the left of each panel shows the distribution of viral mRNAs per cell.
Cells outside the dashed magenta lines have unusually low or high amounts of cellular mRNA (possibly low-quality emulsions or multiplets), and are excluded from subsequent analyses.
{\bf (D)} Distribution across cells of the fraction of all mRNA derived from influenza.
Cells called as infected are in blue, while other cells are in green.
The inset shows the amount of viral mRNA among the human cells called as infected.
{\bf (E)} The number of influenza genes detected per infected cell, and the amount of viral mRNA in cells expressing each number of viral genes.
The majority of cells express all eight gene segments, but a substantial minority fail to express at least one gene.
\FIGSUPP[experiment]{frac_has_gene} shows the frequency that each viral gene is detected in infected cells.
{\bf (F)} Relative expression of viral genes among infected cells.
{\bf (G)} The number of cells infected with wildtype virus, synonymously barcoded virus, or both.
From the cells infected with both viral barcodes, we estimate~\citep{bloom2018estimating} that 63\% of infected cells are co-infected.
{\bf (H)} Fraction of cellular mRNA derived from IFN across all cells, faceted by whether the cells are infected.
Cells to the left of the first dashed magenta line are classified as IFN-, and cells to the right of the second line are classified as IFN+.
Many cells that do not express IFN itself still express ISGs (\FIGSUPP[experiment]{ISG}).
}
\label{fig:experiment}
